### 2014-05-21 prevpub.tex
Add contest

Chapter~\ref{chap:sprout}~also includes material from: A.~Sivaraman,
K.~Winstein, P.~Varley, S.~Das, J.~Ma, A.~Goyal, J.~Batalha, and
H.~Balakrishnan.  \newblock {Protocol Design Contests}.  \newblock
{\em SIGCOMM Computer Communications Review}, July 2014 (forthcoming).

>>>>

Section~\ref{s:cc-contest}~is adapted
from~\cite{cc-contest}: A.~Sivaraman, K.~Winstein, P.~Varley, S.~Das,
J.~Ma, A.~Goyal, J.~Batalha, and H.~Balakrishnan.  \newblock {Protocol
  Design Contests}.  \newblock {\em SIGCOMM Computer Communications
  Review}, July 2014 (forthcoming).
